Global SOC maps and emissions

### 2022-02-28 ResultNotebooks/results_NC.Rmd
Major update of finalized Paper - Draft 2

rev       <- "rev19"
outputdir <- "Output/"

#filesNeeded  <- c("SoilCarbon.rds","Landuse.rds","LanduseChange.rds")
#untar(paste0(getConfig("outputfolder"),"/",rev, "histManagement_ResAllom_2021_01_12_h12_carbonbudget.tgz"), files=filesNeeded, exdir="Data/histManagement_ResAllom", extras="--keep-newer-files ")

# SoilCarbon    <- read.magpie(paste0("Data/histManagement_ResAllom/SoilCarbon.rds"))
# Landuse       <- read.magpie(paste0("Data/histManagement_ResAllom/Landuse.rds"))
# LanduseChange <- read.magpie(paste0("Data/histManagement_ResAllom/LanduseChange.rds"))

SoilCarbon    <- read.magpie(paste0("Data/rev19histManagement/SoilCarbon.rds"))
Landuse       <- read.magpie(paste0("Data/rev19histManagement/Landuse.rds"))
LanduseChange <- read.magpie(paste0("Data/rev19histManagement/LanduseChange.rds"))

>>>>

scenarios <- c("rev27histManagement") #,"rev18histManagement_ResAllom_2021_02_01")
outputdir <- "Output/"

#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon    <- read.magpie(paste0("Data/",scenarios[1],"/SoilCarbon.rds"))
Landuse       <- read.magpie(paste0("Data/",scenarios[1],"/Landuse.rds"))
LanduseChange <- read.magpie(paste0("Data/",scenarios[1],"/LanduseChange.rds"))

### 2022-02-28 ResultNotebooks/results_SOCcompare.Rmd
add revision point by point replies
Major update of finalized Paper - Draft 2

@@

SoilCarbon <- read.magpie("Data/histManagement/SoilCarbon.rds")
Landuse    <- read.magpie("Data/histManagement/Landuse.rds")

@@

SoilCarbon[,,c("naturalstate.crop")] <- SoilCarbon[,,c("naturalstate.natveg")]
SOCStock     <- dimSums(dimSums(SoilCarbon[,,c("naturalstate","actualstate")], dim=3.3)* Landuse, dim=3.2)
cell2reg     <- read.csv("Data/histManagement/ClimateZoneMapping.csv")
reg_SOCStock <- toolAggregate(SOCStock, rel=cell2reg, from="cell", to="IPCC")
```

@@

  WISE       <- readRDS("Data/histManagement/WISE.rds")
  GSOC       <- readRDS("Data/histManagement/GSOC.rds")
  SoilGrids  <- readRDS("Data/histManagement/SoilGrids.rds")
  LPJmL4     <- readRDS("Data/histManagement/LPJmL4.rds")

@@

SOCStock <- reg_SOCStock
reg_SOC  <- mbind(setNames(SOCStock[,"y2010","actualstate"],"This Study"),
                  setNames(SOCStock[,"y2010","naturalstate"],"This Study (PNV)"),
                  setNames(LPJmL4[,"y2010",], "LPJmL4"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"))
glo_SOC <- mbind(setCells(dimSums(reg_SOC, dim=1),"GLO"), reg_SOC)

@@

cols   <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")[c(7,3,1,4,6,8)]

glob <- ggplot(data = melt(subset(table, select =c(Data1, GLO, Year))), aes(y=Year,x=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  scale_size_manual(values=c(4,2,2,2,2,2)) + 
  scale_shape_manual(values=c(19,16,6,2,5,0)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  ylab("") + xlab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.y =element_blank(),
        axis.text.y=element_blank(), 
        legend.position="bottom") + 
  guides(fill=guide_legend(nrow=2,byrow=TRUE))
        #legend.position="right") + guides(fill=guide_legend(ncol=1,byrow=TRUE))

comp <- ggplot(data = melt(subset(table, select=-GLO)), aes(y=Year,x=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  facet_wrap(~ variable, scales="free", drop=TRUE, labeller = label_wrap_gen(width=18)) + 
  scale_size_manual(values=c(4,2,2,2,2,2)) + 
  scale_shape_manual(values=c(19,16,6,2,5,0)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  ylab("") + xlab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        legend.position = "bottom") + guides(fill=guide_legend(nrow=2,byrow=TRUE))

>>>>

rev        <- "rev30"

@@

SoilCarbon <- read.magpie(paste0("Data/", rev, "histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/", rev, "histManagement/Landuse.rds"))

@@

SoilCarbon[,,c("naturalstate.crop")] <- SoilCarbon[,,c("naturalstate.natveg")]
SOCStock     <- dimSums(dimSums(SoilCarbon[,,c("naturalstate","actualstate")], dim=3.3)* Landuse, dim=3.2)
cell2reg     <- read.csv("Data/additional/ClimateZoneMapping.csv")
reg_SOCStock <- toolAggregate(SOCStock, rel=cell2reg, from="cell", to="IPCC")
```

@@

  WISE         <- readRDS(paste0("Data/", rev, "histManagement/WISE.rds"))
  GSOC         <- readRDS(paste0("Data/", rev, "histManagement/GSOC.rds"))
  SoilGrids    <- readRDS(paste0("Data/", rev, "histManagement/SoilGrids.rds"))
  SoilGrids2   <- readRDS(paste0("Data/", rev, "histManagement/SoilGrids2.rds"))
  LPJmL4       <- readRDS(paste0("Data/", rev, "histManagement/LPJmL4.rds"))
  LPJmL4_CRU   <- readRDS(paste0("Data/", rev, "histManagement/LPJmL4_CRU.rds"))
  SOCDebtPaper <- readRDS(paste0("Data/", rev, "histManagement/SOCDebtPaperC.rds"))

@@

SOCStock <- reg_SOCStock
reg_SOC  <- mbind(setNames(SOCStock[,"y2010","actualstate"],"This Study"),
                  setNames(SOCStock[,"y2010","naturalstate"],"This Study (PNV)"),
                  setNames(LPJmL4[,"y2010",], "LPJmL4"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"),
                  setYears(setNames(SoilGrids2[,1,],"SoilGrids2"),"y2010"),
                  setYears(setNames(SOCDebtPaper[,"y2010",],"SOCDebtPaper"),"y2010"))
glo_SOC <- mbind(setCells(dimSums(reg_SOC, dim=1),"GLO"), reg_SOC)

@@

cols   <-c("black",   "#DF536B", "#61D04F", "#2297E6",
           "#28E2E5", "#CD0BBC", "#F5C710", "gray62")[c(2, 7, 1, 3, 4, 5, 6, 8)]

glob <- ggplot(data = melt(subset(table, select =c(Data1, GLO, Year))), aes(y=Year,x=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  scale_size_manual( values = c( 4,  2, 2, 2, 2, 2, 2,  2)) + 
  scale_shape_manual(values = c(19, 16, 6, 2, 5, 0, 8, 10)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  ylab("") + xlab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.y =element_blank(),
        axis.text.y=element_blank(), 
        legend.position="bottom") + 
  guides(fill=guide_legend(nrow=2, byrow=TRUE))
        #legend.position="right") + guides(fill=guide_legend(ncol=1,byrow=TRUE))

comp <- ggplot(data = melt(subset(table, select=-GLO)), aes(y=Year,x=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  facet_wrap(~ variable, scales="free", drop=TRUE, labeller = label_wrap_gen(width=18)) + 
  scale_size_manual( values = c( 4,  2, 2, 2, 2, 2, 2,  2)) + 
  scale_shape_manual(values = c(19, 16, 6, 2, 5, 0, 8, 10)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  ylab("") + xlab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        legend.position = "bottom") + guides(fill=guide_legend(nrow=2,byrow=TRUE))

### 2022-02-28 ResultNotebooks/results_SOCflows.Rmd
Major update of finalized Paper - Draft 2

outputdir <- "Output/"
revfolder <- "Data/histManagement/"

@@

CarbonIn          <- grepSpaceTime(CarbonInflow[,,"crop"]*Landuse[,,"crop"])
CarbonIn          <- mbind(CarbonIn[,,"ag"],CarbonIn[,,"bg"],
                           add_dimension(dimSums(
                             CarbonIn[,,c("livst_chick","livst_egg","livst_milk","livst_pig","livst_rum")], dim=3.1),
                              add="subpool", nm="manure"))

>>>>

outputdir <- "Output/"
revfolder <- "Data/rev30histManagement/"

@@

CarbonIn          <- grepSpaceTime(CarbonInflow[,,"crop"]*Landuse[,,"crop"])
CarbonIn          <- mbind(CarbonIn[,,"ag"],CarbonIn[,,"bg"],
                           add_dimension(dimSums(
                             CarbonIn[,,c("livst_chick","livst_egg","livst_milk","livst_pig","livst_rum")], dim=3.1),
                              add="inputs", nm="manure"))

### 2022-02-28 ResultNotebooks/results_SOCmaps.Rmd
Major update of finalized Paper - Draft 2

rev <- "rev19"
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

@@

for(item in scenarios){
   dir.create(path=paste0("Data/",paste0(rev,item)))
   untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
   files=filesNeeded, exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ")
}

@@

cropland_dens    <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)
cropland_dens[Landuse[,,"crop"]==0] <- NA

cropland_share <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)/dimSums(SoilCarbon[,,"naturalstate"][,,"natveg"], dim=3)
cropland_share[Landuse[,,"crop"]==0] <- NA

cropland_increase <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)-dimSums(SoilCarbon[,,"actualstate"][,,"natveg"], dim=3) 
cropland_increase[Landuse[,,"crop"]==0] <- NA

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-42,0,10),
                     limits = c(-46,0),
                     breaks = c(0, -42, -43, -44, -45, -46),
                     minor_breaks = seq(-2,-42,-2)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

cols          <- colorRampPalette(brewer.pal(11, "RdYlBu"))(7)

SOCshare <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression("cropland SOC stock change factor (unitless)"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

#geom_map(dat=map.world, map = map.world, aes(map_id=region), fill="NA", color="black") +

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression(paste('cropland \u0394SOC in tons of carbon per hectare')), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("< -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

cols <- colorRampPalette(brewer.pal(9, "YlGn"))(8)[2:8]

SOCdensity <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(density2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,150), colours = cols, 
                      name = expression("cropland SOC in tons of carbon per hectare"), 
                      values=c(0,5,10,20,40,70,100,150)/150,
                      breaks=c(5,10,20,40,70,100,150),
                      labels=c("0     5","  10","  20","  40","  70","  100"," >150"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

library(gridExtra)
library(cowplot)
SOCdensity
SOCincrease
SOCemis
SOCshare

grid <- plot_grid(SOCdensity,SOCincrease, SOCshare, SOCemis,  ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCshare.png"),    plot=SOCshare,    width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCincrease.png"), plot=SOCincrease, width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCdensity.png"),  plot=SOCdensity,  width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCemis.png"),     plot=SOCemis,     width = 10, height = 7, dpi = 300, units = "cm")

>>>>

rev <- "rev30"

@@

# for(item in scenarios){
#    dir.create(path=paste0("Data/",paste0(rev,item)))
#    untar(paste0("Data/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ") # files=filesNeeded,
# }

@@

cropland_dens    <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)
cropland_dens[Landuse[,,"crop"] <= 0.001] <- NA

cropland_share <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)/(dimSums(SoilCarbon[,,"naturalstate"][,,"natveg"], dim=3) + 1e-8)
cropland_share[Landuse[,,"crop"] <= 0.001] <- NA

cropland_increase <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)-dimSums(SoilCarbon[,,"actualstate"][,,"natveg"], dim=3) 
cropland_increase[Landuse[,,"crop"] <= 0.001] <- NA

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-34,0,10),
                     limits = c(-40,0),
                     breaks = c(0, -34, -35, -36, -37, -38, -39, -40),
                     minor_breaks = seq(-1,-29,-2)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -36, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

SOCplotmap   <- function(data, name, cols, limits, values = NULL, breaks, labels) {

  out <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(data, Year == "2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits   = limits, 
                      colours  = cols, 
                      name     = name,
                      values   = values,
                      breaks   = breaks,
                      labels   = labels, 
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size=legend_size),
                        direction      = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust    = 0.5,
                        label.hjust    = 1,
                        nrow           = 1,
                        byrow          = F,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          axis.title.x     = element_blank(), 
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7,0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

    return(out)
}

cols        <- colorRampPalette(brewer.pal(11, "RdYlBu"))(11)[c(1:6,7,9,11)]
SOCshare    <- SOCplotmap( data     = share2plot,
                            limits   = c(0,2),
                            cols     = cols,
                            name     = expression("cropland SOC stock change factor (unitless)"),
                            values   = c(0,0.2,0.4,0.6,0.8,1.0,1.2,2)/2,
                            breaks   = c(0.2,0.4,0.6,0.8,1.0,1.2,2),
                            labels   = c("< 0.2","0.4", "0.6","0.8","1.0","1.2","> 1.2"))

SOCincrease <- SOCplotmap( data     = increase2plot,
                            limits   = c(-100, 100),
                            cols     = cols,
                            name     = expression(paste('cropland \u0394SOC in tons of carbon per hectare')),
                            values   = (c(-100, -40, -30, -20, -10, 0, 10, 100)+100)/200,
                            breaks   =  c(-40, -30, -20, -10, 0, 10, 100),
                            labels   = c("< -40", "        -30","        -20","      -10 ","     0","    10","> 10"))

cols <- colorRampPalette(brewer.pal(9, "YlGn"))(8)[2:8]
SOCdensity  <- SOCplotmap( data     = density2plot,
                            limits   = c(0, 150), 
                            cols     = cols, 
                            name     = expression("cropland SOC in tons of carbon per hectare"), 
                            values   = c(0, 5, 10, 20, 40, 70, 100, 150) / 150,
                            breaks   = c(5, 10, 20, 40, 70, 100, 150),
                            labels   = c("0     5","  10","  20","  40","  70","  100"," >150"))

library(gridExtra)
library(cowplot)
SOCemis
SOCincrease
SOCdensity
SOCshare

grid <- plot_grid(SOCemis,SOCdensity,SOCincrease, SOCshare,  ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCshare.png"),    plot=SOCshare,    width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCincrease.png"), plot=SOCincrease, width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCdensity.png"),  plot=SOCdensity,  width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCemis.png"),     plot=SOCemis,     width = 10, height = 7, dpi = 300, units = "cm")
